Figures

### 2020-04-13 manuscript/appendix.Rmd
move figs to separate appendix file

@@

>>>>

How do reported values of lake depth compare to depth calculated from detailed bathymetry?

@@

```{r lgnemanual-vs-bathy-depth, fig.cap="Comparison between reported depth and depth calculated from bathymetry surfaces by US State.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
# see 00_qa.Rmd
knitr::include_graphics("../figures/lgnemanual-vs-bathy-depth-1.pdf")
```
